Algebraic Tori in Unitary Groups

### 2014-10-08 Paper.tex
Minor changes

@@

The map:
\[ H^1(\GalKbK, \Aut(G)) \rightarrow H^1(\GalKbK, \pi_0(\Aut(G))) \]
associates to a form a $G$ a discriminant, that is, a quadratic \'etale algebra $D(G)$.
The map:
\[ H^1(\GalKbK, G^{\rm ad}) \rightarrow H^1(\GalKbK, \pi_1(G^{\rm ad})) \]
associates to $G$ an element of the brauer group $Br(D(G))$ which we call the (class of the) Clifford algebra.
Based on our understanding of $ \pi_1(G^{\rm ad})$ we observe that the Clifford algebra is an algebra with an involution. 
This involution is of the second kind if $n$ is odd, is orthogonal if $n \cong 0 \pmod{4}$ and symplectic otherwise.
Finally, the associated class in:
\[  H^1(\GalKbK, G^{\rm sc}),  \]
which is supported at the real places of $K$, is the index.

@@

>>>>

\TODO{explicit define how to find $\delta$ (norm of an anti-symmetric element cite book of involutions)}

@@

\TODO{explicit define how to find the discriminant (norm of an anti-symmetric element cite book of involutions)}

The map:
\[ H^1(\GalKbK, \Aut(G)) \rightarrow H^1(\GalKbK, \pi_0(\Aut(G))) \]
associates to a form of $G$ a discriminant, that is, a quadratic \'etale algebra $D(G)$.
The map:
\[ H^1(\GalKbK, G^{\rm ad}) \rightarrow H^1(\GalKbK, \pi_1(G^{\rm ad})) \]
associates to $G$ an element of the brauer group $Br(D(G))$ which we call the (class of the) Clifford algebra.
Based on our understanding of $ \pi_1(G^{\rm ad})$ we observe that the Clifford algebra is an algebra with an involution. 
This involution is of the second kind if $n$ is odd, is orthogonal if $n \cong 0 \pmod{4}$ and symplectic otherwise.
Finally, the associated class in:
\[  H^1(\GalKbK, G^{\rm sc}),  \]
which is supported at the real places of $K$, is the index.

@@

\TODO{This currently only covers classical unitary case, do we want to include other classical cases/change the title a bit?}
\TODO{could also put this under 4.4.1}
\TODO{given what we do in 4.4.1 it is important to cover this case}
